Outdated and License-Violating Code on Stack Overflow

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
New title.
Rewrote the conclusions.

\begin{document}
	\title{Are We Reusing Outdated and Licensed Code from Stack Overflow?}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

@@

Online code clones are clones that have been copied to Q\&A websites
such as Stack Overflow. They are similar to classical clones in software
projects where they can be outdated and violating software license but
are much harder to detect. We classified 32,533 clone pairs using our seven patterns of online code
cloning and discovered 112 clone pairs that have been copied, with
evidence, from Qualitas projects to Stack Overflow, 197 clone
pairs that have been copied from external sources besides Qualitas to
Stack Overflow, and 359 clone pairs that are highly similar but
without evidence of copying.

We performed a detailed analysis of the online
clone pairs on two aspects: outdated code and
licensing violation. The investigation of the 112 clone pairs from Qualitas
to Stack Overflow reveals that 64 of them are outdated. 
Moreover, we found 358 code snippets on Stack Overflow that violate
the license of their original software.

>>>>

\begin{document}
	\title{Outdated and License-Violating Code on Stack Overflow}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

@@

Online code clones are clones that have been copied to Q\&A websites
such as Stack Overflow. 
% They are similar to classical clones in software
% projects where they can be outdated and violating software license but
% are much harder to detect. 
We classified 32,533 clone pairs using seven patterns of online code
cloning.  After automatically removing boiler-plate clones, we
manually investigated 3,636 clone pairs. In the 1,216 manually
confirmed clone pairs, we discovered 112 clone pairs that have been
copied, with evidence, from Qualitas projects to Stack Overflow, 197
clone pairs that have been copied from external sources besides
Qualitas to Stack Overflow, and 359 clone pairs that are highly
similar but without evidence of copying.

We performed a detailed analysis of the online clone pairs on two
aspects: outdated code and licensing violation. The investigation of
the 112 clone pairs copied, with evidence, from Qualitas to Stack
Overflow reveals that 64 of them are outdated.  Moreover, we found 358
code snippets on Stack Overflow that violate the license of their
original software.
